Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-10 authorinstr_2.tex
Tag Based Update 1

An overview of the API structure and some useful fields:
\begin{enumerate}
\item \textbf{Tweets} The short messages consisting of 140 characters sent by users
	\subitem \textbf{Coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
	\subitem \textbf{Entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
	\subitem \textbf{Lang} Returns the language in which a tweet has been sent
	\subitem \textbf{User} Returns the user that sent a tweet
\item \textbf{Users} The users that send the tweets
	\subitem \textbf{Description} Returns the description that the user defined for his account
	\subitem \textbf{Location} Returns the location that the user defined for his account
	\subitem \textbf{Status} Returns, if possible, the user's latest tweet
\item \textbf{Entities} Images, hashtags and other entities that tweets can hold
	\subitem \textbf{Hashtags} Returns the hashtags that have been parset out of a tweet
	\subitem \textbf{Media} Returns the media that is associated with a tweet
	\subitem \textbf{urls} Returns the urls embedded in a tweet
	\subitem \textbf{user\_mentions} Returns the users that have been mentioned in a tweet
\item \textbf{Places} Predefined places on Twitter that users can associate with
	\subitem \textbf{Country} Returns the country associated with a place
	\subitem \textbf{Full\_name} Returns the full name of a place, for example Kanses ``City, Kansas''
	\subitem \textbf{Place\_type} Returns the type of a place, for example ``city''
\end{enumerate}

@@

Twitter allows their users to contribute their own social annotations to their tweets in the form of tags. These tags can be arbitrarily generated by users 
which make them hold interesting information about both the tweet and the user that posted it.

@@

%TODO: Technische stuff begrijpen zodat ik die hier neer kan zetten + bibliography laten doorverwijzen

>>>>

An overview of the API structure and some useful fields:
\begin{enumerate}
\item \textbf{Tweets} The short messages consisting of 140 characters sent by users
	\subitem \textbf{coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
	\subitem \textbf{entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
	\subitem \textbf{lang} Returns the language in which a tweet has been sent
	\subitem \textbf{user} Returns the user that sent a tweet
\item \textbf{Users} The users that send the tweets
	\subitem \textbf{description} Returns the description that the user defined for his account
	\subitem \textbf{location} Returns the location that the user defined for his account
	\subitem \textbf{status} Returns, if possible, the user's latest tweet
\item \textbf{Entities} Images, hashtags and other entities that tweets can hold
	\subitem \textbf{hashtags} Returns the hashtags that have been parset out of a tweet
	\subitem \textbf{media} Returns the media that is associated with a tweet
	\subitem \textbf{urls} Returns the urls embedded in a tweet
	\subitem \textbf{user\_mentions} Returns the users that have been mentioned in a tweet
\item \textbf{Places} Predefined places on Twitter that users can associate with
	\subitem \textbf{country} Returns the country associated with a place
	\subitem \textbf{full\_name} Returns the full name of a place, for example Kanses ``City, Kansas''
	\subitem \textbf{place\_type} Returns the type of a place, for example ``city''
\end{enumerate}

@@

Twitter allows their users to contribute their own social annotations to their tweets in the form of tags. These tags can be arbitrarily generated by users 
which make them hold interesting information about both the tweet and the user that posted it. There are two dominant techniques that are currently being
used by researchers to model the information of tagged based analysis, The Linear-Weighted Hybrid Model, and the Pair-wise Interaction Tensor Factorisation Model.

@@

The Linear-Weighted Hybrid model uses the tags as recommendation components whose output is a weighted sum of components $\kappa_1$ through $\kappa_k$. 
Each component $\kappa_i$ has its own value between 0 and 1 computed by the function $\phi_i (u,q,r)$, and a corresponding weight $\alpha_i$, also between
0 and 1. The sum of all weights $\alpha_i$ has to be 1.

Therefore, the hybrid model is defined as the function $\varphi (u, q, r) = \sum\limits_{i = 1}^k \alpha_i \phi_i (u,q,r)$

All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique. A subset is used as a holdout set, and a vector
gets created with random weights that sum to 1. The recommender then modifies the vector over the holdout set to train the algorithm until it reaches
a stable point. The algorithm then restarts to avoid local minima.
